\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-06-18 SuppMat.tex
Updates from Overleaf

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{adjustbox}   
%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

@@

\section{ Cordero~\emph{et al} dataset}
\subsection{Structure prediction ordered by RNA}

@@

\begin{table}[h]

@@

%\section{IPANEMAP Vs Rsample}
\section{Hadjin ~\emph{et al} dataset}

  \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llllHllH}
\toprule
\textbf{RNA} & Length &  \multicolumn{3}{l}{\Software{Rsample}} &  \multicolumn{3}{l}{\Software{IPANEMAP}} \\
\midrule
	&		&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	\\
A	&	34	&	0.625	&	1	&	0.791	&	0.625	&	1	&	0.791	\\
B	&	530	&	0.6622	&	0.6203	&	0.641	&	0.8986	&	0.8062	&	0.851	\\
C	&	301	&	0.03	&	0.0313	&	0.031	&	0.6	&	0.6	&	0.6	\\
D	&	214	&	0.6349	&	0.6667	&	0.651	&	0.7302	&	0.8519	&	0.789	\\
E	&	500	&	0.6382	&	0.7823	&	0.707	&	0.5263	&	0.5517	&	0.539	\\
F	&	47	&	0.4	&	0.75	&	0.548	&	0.6	&	0.75	&	0.671	\\
G	&	118	&	0.7179	&	0.8	&	0.758	&	0.7692	&	0.8333	&	0.801	\\
H	&	76	&	0.4762	&	0.5556	&	0.514	&	0.7619	&	0.7619	&	0.762	\\
I	&	155	&	0.6786	&	0.8261	&	0.749	&	0.9821	&	0.9821	&	0.982	\\
J	&	79	&	0.7727	&	0.85	&	0.81	&	0.9545	&	0.875	&	0.914	\\
K	&	71	&	1	&	1	&	1	&	1	&	0.9545	&	0.977	\\
L	&	66	&	0.5625	&	0.6923	&	0.624	&	0.625	&	0.7143	&	0.668	\\
M	&	79	&	0.6538	&	0.8095	&	0.727	&	0.6538	&	0.68	&	0.667	\\
N	&	120	&	0.2857	&	0.2632	&	0.274	&	0.9714	&	0.9189	&	0.945	\\
O	&	97	&	0.9286	&	0.9286	&	0.929	&	0.9286	&	0.8966	&	0.912	\\
P	&	511	&	0.9328	&	0.7762	&	0.851	&	0.8908	&	0.7681	&	0.827	\\
Q	&	401	&	0.5826	&	0.5583	&	0.57	&	0.7304	&	0.75	&	0.74	\\
R	&	425	&	0.8397	&	0.8271	&	0.833	&	0.9084	&	0.8815	&	0.895	\\
S	&	336	&	0.5481	&	0.6129	&	0.58	&	0.8077	&	0.866	&	0.836	\\
T	&	473	&	0.7986	&	0.7143	&	0.755	&	0.8819	&	0.8194	&	0.85	\\
U	&	412	&	0.5379	&	0.6174	&	0.576	&	0.75	&	0.8462	&	0.797	\\
V	&	75	&	0.619	&	0.6842	&	0.651	&	0.619	&	0.5652	&	0.591	\\
W	&	174	&	0.8095	&	0.8644	&	0.836	&	0.8095	&	0.9808	&	0.891	\\
X	&	154	&	0.875	&	0.913	&	0.894	&	0.875	&	0.913	&	0.894	\\

\bottomrule
\end{tabular}
\end{adjustbox}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

 \begin{table}[h]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}ll@{}}
 \toprule
Rna ID & Description\\
 \midrule
A	&	PreQ1riboswitchBsubtilis\\
B	&	5domainof16SrRNAEcoli\\
C	&	SignalrecognitonparticleRNAhuman\\
D	&	GroupIintronAzoarcussp\\
E	&	HIV15primepseudoknotdomain\\
F	&	Telomerasepseudoknothuman\\
G	&	SAMIriboswitchTtengcongensis\\
H	&	tRNApheEcoli\\
I	&	P546domainbI3groupIintron\\
J	&	TPPriboswitchEcoli\\
K	&	AdenineriboswitchVvulnificus\\
L	&	FluorideriboswitchPsyringae\\
M	&	SARScoronaviruspseudoknot\\
N	&	5SrRNAEcoli\\
O	&	cyclicdiGMPriboswitchVcholerae\\
P	&	5domainof23SrRNAEcoli\\
Q	&	RNasePBsubtilis\\
R	&	GroupIIntronTthermophila\\
S	&	HepatitisCvirusIRESdomain\\
T	&	5domainof16SrRNAHvolcanii\\
U	&	GroupIIintronOiheyensis\\
V	&	tRNAaspyeast\\
W	&	LysineriboswitchTmaritime\\
X	&	MBoxriboswitchBsubtilis\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{24 RNAs from Hadjin \emph{ et al.} dataset.}
\label{clyu}

\end{table}
%  \Heatset{min=0,  
%	max=1,   
%	max colour=Aquamarine3, % colour at maximum
%	min colour=BadCol,      % colour at minimum
%	Min colour=BadCol, % colour for values below min
%	Max colour=Aquamarine3   % colour for values above max
%}

\begin{table}
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llHHHHHHHHHHHlHH}
\toprule
\textbf{RNA} & Length &  \multicolumn1c{Run1} &\multicolumn1c{Run2}&\multicolumn1c{Run3}&\multicolumn1c{Run4}&\multicolumn1c{Run5}&\multicolumn1c{Run6}&\multicolumn1c{Run7}&\multicolumn1c{Run8}&\multicolumn1c{Run9}&\multicolumn1c{Run10}& \multicolumn1c{Average}& \multicolumn1c{Sd}&\multicolumn1c{\textbf{MFE-RNAfold}} & \multicolumn1c{\textbf{MEA-RNAfold}}\\
\midrule

@@

\section{Lariat capping ribozyme in {\itshape Didymium iridis}}
\begin{table}
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{lHHHHHHHHHHHHHHHHH}
\toprule
&&\multicolumn{1}{l}{1M7ILUMg}  &\multicolumn{1}{l}{1M7ILU } &\multicolumn{1}{l}{NMIAMg}  &\multicolumn{1}{l}{NMIA } &\multicolumn{1}{l}{1M7ILU3Mg}  &\multicolumn{1}{l}{NMIAMgCE}  &\multicolumn{1}{l}{NaiMg} &\multicolumn{1}{l}{BzCNMg } &\multicolumn{1}{l}{1M7MgCE}&\multicolumn{1}{l}{CMCTMg}  &\multicolumn{1}{l}{1M7ILU3}  &\multicolumn{1}{l}{DMSMg}&\multicolumn{1}{l}{NMIACE }&\multicolumn{1}{l}{1M7CE}&\multicolumn{1}{l}{BzCN}&\multicolumn{1}{l}{Nai}  \\
\midrule
&&0.85&0.84&0.81&0.8&0.74&0.73&0.73&0.71&0.7&0.7&0.64&0.63&0.61&0.6&0.6&0.6\\
1M7ILUMg  &0.85&0.85&0.84&0.8&0.82&0.82&0.82&0.75&0.79&0.78&0.79&0.79&0.85&0.61&0.79&0.79&0.85\\
1M7ILU  &0.84&&0.84&0.82&0.82&0.7&0.83&0.72&0.82&0.85&0.83&0.84&0.84&0.84&0.6&0.84&0.6\\
NMIAMg  &0.81&&&0.81&0.8&0.74&0.82&0.82&0.81&0.81&0.79&0.8&0.8&0.61&0.81&0.81&0.6\\
NMIA  &0.8&&&&0.8&0.74&0.73&0.81&0.78&0.7&0.79&0.63&0.72&0.61&0.7&0.7&0.59\\
1M7ILU3Mg  &0.74&&&&&0.74&0.74&0.7&0.74&0.74&0.7&0.63&0.74&0.74&0.74&0.74&0.74\\
NMIAMgCE  &0.73&&&&&&0.73&0.73&0.73&0.73&0.73&0.61&0.73&0.61&0.73&0.73&0.6\\
NaiMg &0.73&&&&&&&0.73&0.72&0.7&0.73&0.64&0.68&0.61&0.73&0.73&0.59\\
BzCNMg  &0.71&&&&&&&&0.71&0.65&0.73&0.63&0.72&0.6&0.61&0.6&0.59\\
1M7MgCE&0.7&&&&&&&&&0.7&0.7&0.7&0.7&0.61&0.61&0.6&0.6\\
CMCTMg  &0.7&&&&&&&&&&0.7&0.63&0.74&0.61&0.6&0.6&0.6\\
1M7ILU3  &0.64&&&&&&&&&&&0.64&0.62&0.62&0.65&0.65&0.59\\
DMSMg&0.63&&&&&&&&&&&&0.63&0.61&0.6&0.6&0.6\\
NMIACE&0.61&&&&&&&&&&&&&0.61&0.62&0.6&0.6\\
1M7CE&0.6&&&&&&&&&&&&&&0.6&0.61&0.59\\
BzCN&0.6&&&&&&&&&&&&&&&0.6&0.6\\
Nai  &0.6&&&&&&&&&&&&&&&&0.6\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{MCC of predicted structures with \OurTool{} in the case of Bi-probing}.
\end{table}

\begin{table}
\newcommand{\MyScale}{.2}
\begin{tabular}{@{}cccc@{}}

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
1M7ILU&1M7ILUMg&1M7MgCE&NaiMg\\
+NMIAMg&+1M7ILU3Mg&+NMIAMgCE&+CMCTMg\\
\end{tabular}
\caption{Predicted structures with conditions belonging to the same cluster}
\end{table}

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{adjustbox}   
%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

@@

\section{Detailed results on Cordero~\emph{et al} dataset}
\subsection{Structure prediction ordered by RNA}

@@

\begin{table}[H]

@@

\newpage

%\section{IPANEMAP Vs Rsample}
\section{Detailed results on Hadjin~\emph{et al} dataset}

 \begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}ll@{}}
 \toprule
RNA ID & Description\\
 \midrule
A	&	PreQ1riboswitchBsubtilis\\
B	&	5domainof16SrRNAEcoli\\
C	&	SignalrecognitonparticleRNAhuman\\
D	&	GroupIintronAzoarcussp\\
E	&	HIV15primepseudoknotdomain\\
F	&	Telomerasepseudoknothuman\\
G	&	SAMIriboswitchTtengcongensis\\
H	&	tRNA phe Ecoli\\
I	&	P546domainbI3groupIintron\\
J	&	TPPriboswitchEcoli\\
K	&	AdenineriboswitchVvulnificus\\
L	&	FluorideriboswitchPsyringae\\
M	&	SARScoronaviruspseudoknot\\
N	&	5SrRNAEcoli\\
O	&	cyclicdiGMPriboswitchVcholerae\\
P	&	5domainof23SrRNAEcoli\\
Q	&	RNasePBsubtilis\\
R	&	GroupIIntronTthermophila\\
S	&	HepatitisCvirusIRESdomain\\
T	&	5domainof16SrRNAHvolcanii\\
U	&	GroupIIintronOiheyensis\\
V	&	tRNAaspyeast\\
W	&	LysineriboswitchTmaritime\\
X	&	MBoxriboswitchBsubtilis\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{24 RNAs from Hadjin \emph{ et al.} dataset.}
\label{clyu}

  \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llllHllH}
\toprule
\textbf{RNA} & Length &  \multicolumn{3}{l}{\Software{Rsample}} &  \multicolumn{3}{l}{\Software{IPANEMAP}} \\
\midrule
	&		&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	&	Sensitivity	&	PPV	&	\multicolumn1c{GM}	\\
A	&	34	&	0.625	&	1	&	0.791	&	0.625	&	1	&	0.791	\\
B	&	530	&	0.6622	&	0.6203	&	0.641	&	0.8986	&	0.8062	&	0.851	\\
C	&	301	&	0.03	&	0.0313	&	0.031	&	0.6	&	0.6	&	0.6	\\
D	&	214	&	0.6349	&	0.6667	&	0.651	&	0.7302	&	0.8519	&	0.789	\\
E	&	500	&	0.6382	&	0.7823	&	0.707	&	0.5263	&	0.5517	&	0.539	\\
F	&	47	&	0.4	&	0.75	&	0.548	&	0.6	&	0.75	&	0.671	\\
G	&	118	&	0.7179	&	0.8	&	0.758	&	0.7692	&	0.8333	&	0.801	\\
H	&	76	&	0.4762	&	0.5556	&	0.514	&	0.7619	&	0.7619	&	0.762	\\
I	&	155	&	0.6786	&	0.8261	&	0.749	&	0.9821	&	0.9821	&	0.982	\\
J	&	79	&	0.7727	&	0.85	&	0.81	&	0.9545	&	0.875	&	0.914	\\
K	&	71	&	1	&	1	&	1	&	1	&	0.9545	&	0.977	\\
L	&	66	&	0.5625	&	0.6923	&	0.624	&	0.625	&	0.7143	&	0.668	\\
M	&	79	&	0.6538	&	0.8095	&	0.727	&	0.6538	&	0.68	&	0.667	\\
N	&	120	&	0.2857	&	0.2632	&	0.274	&	0.9714	&	0.9189	&	0.945	\\
O	&	97	&	0.9286	&	0.9286	&	0.929	&	0.9286	&	0.8966	&	0.912	\\
P	&	511	&	0.9328	&	0.7762	&	0.851	&	0.8908	&	0.7681	&	0.827	\\
Q	&	401	&	0.5826	&	0.5583	&	0.57	&	0.7304	&	0.75	&	0.74	\\
R	&	425	&	0.8397	&	0.8271	&	0.833	&	0.9084	&	0.8815	&	0.895	\\
S	&	336	&	0.5481	&	0.6129	&	0.58	&	0.8077	&	0.866	&	0.836	\\
T	&	473	&	0.7986	&	0.7143	&	0.755	&	0.8819	&	0.8194	&	0.85	\\
U	&	412	&	0.5379	&	0.6174	&	0.576	&	0.75	&	0.8462	&	0.797	\\
V	&	75	&	0.619	&	0.6842	&	0.651	&	0.619	&	0.5652	&	0.591	\\
W	&	174	&	0.8095	&	0.8644	&	0.836	&	0.8095	&	0.9808	&	0.891	\\
X	&	154	&	0.875	&	0.913	&	0.894	&	0.875	&	0.913	&	0.894	\\

\bottomrule
\end{tabular}
\end{adjustbox}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}
\newpage

%  \Heatset{min=0,  
%	max=1,   
%	max colour=Aquamarine3, % colour at maximum
%	min colour=BadCol,      % colour at minimum
%	Min colour=BadCol, % colour for values below min
%	Max colour=Aquamarine3   % colour for values above max
%}

\begin{table}[H]
\begin{adjustbox}{max width=.9\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llHHHHHHHHHHHlHH}
\toprule
\textbf{RNA} & Length &  \multicolumn1c{Run1} &\multicolumn1c{Run2}&\multicolumn1c{Run3}&\multicolumn1c{Run4}&\multicolumn1c{Run5}&\multicolumn1c{Run6}&\multicolumn1c{Run7}&\multicolumn1c{Run8}&\multicolumn1c{Run9}&\multicolumn1c{Run10}& \multicolumn1c{Average}& \multicolumn1c{Sd}&\multicolumn1c{\textbf{MFE-RNAfold}} & \multicolumn1c{\textbf{MEA-RNAfold}}\\
\midrule

@@

\newpage 
\section{Detailed results of Lariat capping ribozyme from {\itshape Didymium iridis}}

\begin{table}[H]
 \Heatset{min=0.2,  
	max=.5,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
\begin{center}

\begin{tabular}{lHH}
 & \multicolumn2c{Distance of probing profile}\\
Condition & \multicolumn1c{vs prediction}&\multicolumn1c{vs native}\\
\toprule
1M7ILUMg & 0.234 & 0.2872\\
1M7ILU &	0.2784 & 0.2961\\
NMIAMg &	0.2606 & 0.2518\\
NMIA &	0.2961 & 0.3316\\
1M7ILU3Mg &	0.4291 & 0.3936\\
NMIAMgCE &	0.4291 & 0.3404\\
NaiMg 	& 0.3493 & 0.305\\
BzCNMg & 	0.3759 & 0.2429\\
1M7MgCE &	0.4379 & 0.3759\\
CMCTMg &	0.4911 & 0.4113\\
1M7ILU3 &	0.2961 & 0.3404\\
DMSMg &	0.3493 & 0.3227\\
NMIACE 	&0.2695 &0.2518 \\
1M7CE &	0.3582 & 	0.3316\\
BzCN &	0.4911 & 	0.4734\\
Nai &	0.4025 &0.4025\\
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

\begin{table}[H]
\newcommand{\MyScale}{.18}
\begin{tabular}{@{}ccccc@{}}

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/native_structure}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
Native&1M7ILU&1M7ILUMg&1M7MgCE&NaiMg\\
structure &+NMIAMg&+1M7ILU3Mg&+NMIAMgCE&+CMCTMg\\
\end{tabular}
\caption{Predicted structures with conditions belonging to the same cluster}
\end{table}

\begin{table}[H]
\begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{lHHHHHHHHHHHHHHHHH}
\toprule
&&\multicolumn{1}{l}{1M7ILUMg}  &\multicolumn{1}{l}{1M7ILU } &\multicolumn{1}{l}{NMIAMg}  &\multicolumn{1}{l}{NMIA } &\multicolumn{1}{l}{1M7ILU3Mg}  &\multicolumn{1}{l}{NMIAMgCE}  &\multicolumn{1}{l}{NaiMg} &\multicolumn{1}{l}{BzCNMg } &\multicolumn{1}{l}{1M7MgCE}&\multicolumn{1}{l}{CMCTMg}  &\multicolumn{1}{l}{1M7ILU3}  &\multicolumn{1}{l}{DMSMg}&\multicolumn{1}{l}{NMIACE }&\multicolumn{1}{l}{1M7CE}&\multicolumn{1}{l}{BzCN}&\multicolumn{1}{l}{Nai}  \\
\midrule
&&0.85&0.84&0.81&0.8&0.74&0.73&0.73&0.71&0.7&0.7&0.64&0.63&0.61&0.6&0.6&0.6\\
1M7ILUMg  &0.85&0.85&0.84&0.8&0.82&0.82&0.82&0.75&0.79&0.78&0.79&0.79&0.85&0.61&0.79&0.79&0.85\\
1M7ILU  &0.84&&0.84&0.82&0.82&0.7&0.83&0.72&0.82&0.85&0.83&0.84&0.84&0.84&0.6&0.84&0.6\\
NMIAMg  &0.81&&&0.81&0.8&0.74&0.82&0.82&0.81&0.81&0.79&0.8&0.8&0.61&0.81&0.81&0.6\\
NMIA  &0.8&&&&0.8&0.74&0.73&0.81&0.78&0.7&0.79&0.63&0.72&0.61&0.7&0.7&0.59\\
1M7ILU3Mg  &0.74&&&&&0.74&0.74&0.7&0.74&0.74&0.7&0.63&0.74&0.74&0.74&0.74&0.74\\
NMIAMgCE  &0.73&&&&&&0.73&0.73&0.73&0.73&0.73&0.61&0.73&0.61&0.73&0.73&0.6\\
NaiMg &0.73&&&&&&&0.73&0.72&0.7&0.73&0.64&0.68&0.61&0.73&0.73&0.59\\
BzCNMg  &0.71&&&&&&&&0.71&0.65&0.73&0.63&0.72&0.6&0.61&0.6&0.59\\
1M7MgCE&0.7&&&&&&&&&0.7&0.7&0.7&0.7&0.61&0.61&0.6&0.6\\
CMCTMg  &0.7&&&&&&&&&&0.7&0.63&0.74&0.61&0.6&0.6&0.6\\
1M7ILU3  &0.64&&&&&&&&&&&0.64&0.62&0.62&0.65&0.65&0.59\\
DMSMg&0.63&&&&&&&&&&&&0.63&0.61&0.6&0.6&0.6\\
NMIACE&0.61&&&&&&&&&&&&&0.61&0.62&0.6&0.6\\
1M7CE&0.6&&&&&&&&&&&&&&0.6&0.61&0.59\\
BzCN&0.6&&&&&&&&&&&&&&&0.6&0.6\\
Nai  &0.6&&&&&&&&&&&&&&&&0.6\\
\bottomrule
\end{tabular}
\end{adjustbox}
\caption{MCC of predicted structures with \OurTool{} in the case of Bi-probing}.
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{ll}
Sample size & MCC\\
\toprule

100 & 0.55 \\
500 & 0.55  \\
1000 &  0.81\\
2000 & 	0.55  \\
3000 &  0.77 \\
5000 & 	0.55  \\ 
10000& 0.8 \\
\end{tabular}
\end {center}
\caption{ MCC of predicted structures in absence of probig data when varyingthe sample size }
\end{table}
